---
title: "File Combination and For loops"
author: "Michael Puerto"
date: "11/16/2020"
output: html_document
---

First we need to read in the data, at least one file, to see what it looks like



```{r}
if (!require(pacman)) install.packages("pacman") 
pacman::p_load(tidyverse,readr,lubridate)



# Don't forget, this is my own directory, we need to change this later to work with the data directly from github if possible


one_file = read_csv("C:/Users/macia/Documents/MSIA-19/Git/Green_Hackathon-Fall2020/data/Analysis/Baseball_results.csv")

glimpse(one_file)

```
We will need the building name as well as the specific meter
Ok so each file format should be the same. The only thing that is missing "building name". I think at first, I'll just try to combine all the files using a for loop.

After that is working, adjust the forloop to add the file name. If you notice, they way the file names are formated .. __*building name*_reults.csv__




```{r, message=FALSE, warning=FALSE,error=FALSE}

# Don't forget, this is my own directory, we need to change this later to work with the data directly from github if possible
#
directory = "C:/Users/macia/Documents/MSIA-19/Git/Green_Hackathon-Fall2020/data/Analysis/"

file_names <- dir(directory) # get file names of the directory

data = NULL # to store the results of our data late

for (i in file_names){# for each file in the directory (i)
   if (i == "Meter Names and Labels.xlsx"){
     next
   }
  local_path = paste(directory, i, sep = "") # "glue"/paste the directory and file name
  data_temp = read_csv(local_path) # read in thee data
  data_temp['building'] = i # create a new variable in the data of the file name -> since this contains building name
  # this "building name" would read baseball_results.csv 
  data_temp['building'] = sub("_results.*","",data_temp$building) # I replace _results.csv with "" (empty) leaving only the building name left
  data = bind_rows(data,data_temp) # bind results to dataframe outside of the loop. 
}



#write.csv(data,"combined_results.csv") # this will write the csv. 


```


Now let's take a look :)


```{r}
glimpse(data)
```

Now we have 3.6 million observations! 
Phenomenal!
How many data points in each building?

```{r}

data %>% group_by(building) %>% count(sort = T)

```

Here we read in the labels and clean up the labels so that we can join them with the larger data later. 

```{r}

p_load(readxl)
labels = read_xlsx("C:/Users/macia/Documents/MSIA-19/Git/Green_Hackathon-Fall2020/data/Analysis/Meter Names and Labels.xlsx",col_types = "text",trim_ws = T)



labels['better_name'] = gsub("'","",labels$Name,) # gsub will replace all ' <- with "" (empty)

labels <- labels %>%  mutate(better_name = case_when(
  str_detect(Label,"North & South Spencer Residence Hall")	~  "Spencer", # the 'name' on the label set is different than the file name. This will detect if the character matches and change it to desried string -> one that matches the file name.  
  str_detect(Name,"JacksonLibraryTower_kWh") ~ "JacksonLibraryTower",
  TRUE ~ as.character(better_name))) %>% # returns the names as normal
  mutate(better_name = str_trim(better_name, side = "both"),
         "better_label" =gsub("'","",labels$Label))%>% 
  mutate(better_label = str_trim(better_label,side = "both"))# remove white space on bothsides of the word




```


This will join the tables/dataframe also create year, month, day of the month, week of the year and day of the week columns. 

```{r}

data <- data %>% inner_join(labels, by = c("building" = "better_name")) %>% select(-c(building,Name)) # inner join on the names. 

data <- data %>% mutate("Year" = year(Datetime), #create year variable
                "Month" = month(Datetime), #create month variable
                "Day of the month" = day(Datetime),  #create day of the month variable
                "Week of the year" = week(Datetime),  #create week of the year variable 
                "Day of the week" = wday(Datetime, label = T)) #create day of the week variable


# The following code is just to verify that we did everything right. For example, shoud have 7 days in a week, 31 days in a month, 53 weeks in a year.. etc

data %>%  distinct(Year) %>% arrange(Year)
data %>%  distinct(Month) %>% arrange(Month)
data %>%  distinct(`Week of the year`) %>% arrange(`Week of the year`)
data %>%  distinct(`Day of the month`) %>% arrange(`Day of the month`)
data %>%  distinct(`Day of the week`) %>% arrange(`Day of the week`)
```

Next is to get lon and lat of buildings? 
Also get dimentions of the buildings? 
Also need to find a place to put the data, so that we can easily retrive it -> git large file storage? 

```{r}


# to conserve memory, let's get rid of the 'duplicate'.. not really dupe, names

#combined_results <- combined_results %>% select(-c(Label))

#write.csv(combined_results,"combined_results.csv") # this will write the csv. 

#getwd()

```


