---
title: "TotalConsumptionChart1"
author: "Jazarai Sturdivant"
date: "11/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Questions to be explored: 

What is the total amount of energy being consumed??
By type of use(what types of tasks?)
By building
By room
By region of the campus
By time of day (hours or qualitative description of time, during business hours/not)

*Mowgli- Does the time period of the construction of the building relate to energy consumption?
*


```{r libraries}

library(readr)
library(here)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(scales)

```

## What is the total amount of energy being consumed? 


```{r }

Baseball_results <- read_csv("/cloud/project/Code/Data/Baseball_results.csv")
str(Baseball_results)
                             
```
```{r }
#Create table by year of consumption
my2015Baseball_results <- Baseball_results %>%
  select(Datetime, Actual, Predicted)%>%
  filter(year(Datetime) == "2015")

#View(myBaseball_results)      

```


```{r}

EnergyConsumption15 <- ggplot(Baseball_results)+
  geom_col(aes(x = Datetime, y = Actual), colour = "#ffb71b") +    #using UNCG gold rgb(255,183,27)
  geom_col(aes(x = Datetime, y = Predicted), colour = "#0f2044") #using UNCG blue rgb(15,32,68)

EnergyConsumption15

# Need to add filter for each or the time units (will interactivity allow for this?)

```




```{r}

TotalConsumption <- Baseball_results %>%
  select(Datetime, Actual, Predicted)%>%
  group_by(Year = year(Datetime)) %>%
  summarize(TotalConsumed = sum(Actual), TotalPrediction = sum(Predicted))

TotalConsumption

```


```{r}

CumulativeConsumption <- ggplot(TotalConsumption)+
  geom_line(aes(x = Year, y = TotalConsumed), colour = "#ffb71b") +    #using UNCG gold rgb(255,183,27)
  geom_line(aes(x = Year, y = TotalPrediction), colour = "#0f2044")


CumulativeConsumption


```


```{r}

TimeEnergyConsumption15 <- ggplot(Baseball_results)+
  geom_col(aes(x = Datetime, y = Actual), colour = "#ffb71b") +    #using UNCG gold rgb(255,183,27)
  geom_col(aes(x = Datetime, y = Predicted), colour = "#0f2044")+ #using UNCG blue rgb(15,32,68)
scale_y_continuous(labels = paste0(ylab, "K"),
                     breaks = 10^6 * ylab)

TimeEnergyConsumption15


```


```{r}
AverageEnergyConsumption <- Baseball_results %>%
  select(Datetime, Actual, Predicted)%>%
  group_by(Year = year(Datetime)) %>%
  summarize(AverageConsumed = mean(Actual), AveragePredicted = mean(Predicted))

AverageEnergyConsumption

```



```{r}

HourlyEnergyConsumption15 <- ggplot(AVerageEnergyConsumption)+
  geom_point(aes(x = Year, y = AverageConsumed), colour = "#ffb71b") +    #using UNCG gold rgb(255,183,27)
  geom_point(aes(x = Year, y = AveragePredicted), colour = "#0f2044") #using UNCG blue rgb(15,32,68)

HourlyEnergyConsumption15



```






